Concurrent Programming with CXL

### 2020-06-15 book/paper.tex
Latest
Added citation to the little book of semaphores

@@

@@

>>>>

You may find the free ``The Little Book of Semaphores'' by
Allen Downey a great resource for working with semaphores.
You can find it at
\underline{http://greenteapress.com/semaphores/LittleBookOfSemaphores.pdf}.

@@

Andrew Birrell's paper on Programming with Threads gives an excellent
introduction to working with Mesa-style condition variables~\cite{Birrell89}.

@@

\begin{quote}
\begin{itemize}
\item See if you can implement barrier synchronization for $N$ processes
with just three semaphores.  Busy waiting is not allowed.
\item How about just two?
\end{itemize}
\end{quote}
